Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-14 doc/reviews/ResponseToReviewer1.tex

\noindent
\comment{The membrane rupture situation, briefly illustrated in Section
4.2.3, is not investigated at all. Is there a dimensionless number
related to this phenomenon with a critical value above which rupture
happens? (e.g.~quantifying the competition between shear and
attraction)}

\noindent
\comment{I understand that the results of Section 4.4 are mostly
qualitative and that the goal is to show the visual agreement between
the coarse-grained and continuum vesicle models, but it would be
insightful to provide quantitative comparisons to measure how close they
are to each other.}
\begin{itemize}
  \item We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript. We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the corresopnding movie is added as a supplementary material. We also included the description in the section of membrane rupture.
\end{itemize}

\noindent
\comment{The problem is not nondimensionalized with the characteristic
scales of the system but with ns, nm and $\text{pN} \cdot
\text{nm}^{-2}$. This (unusual) nondimensionalization makes it hard to
compare physical quantities and to define order parameters that would
explain/characterize some phenomena observed in the simulations
(e.g.~the membrane rupture).}

\begin{itemize}
  \item We thank the Reviewer to point this out. There is a significant difference between 
the proposed model in the manuscript and other continuum models in literatures. For example, refer to \emph{Rahimian, et al., J. Comput. Phys., 2011}, the 
provided time scale is $\tau = \mu R_0^3/\kappa_B$ where $\mu$ the fluid viscosity and $\kappa_B$ the bending modulus. $R_0$ is the initial radius of the reference vesicle. Since the bending modulus does not play any roles in the proposed model, we then scaled time unit with a realistic characteristic time ns. With the use of the detailed scaling laws described in section 4.1, we aim to have comparable
numerical results against the experiments. Moreover, if we attempt to calculate the characterstic 
time scale using characteristic length and energy scales, it will also result a vaule of order ns. 
Since the system involves multiple length scales, diameter of the particle $l_0$ and size of the JP
vesicle $R_0$, we decided to use ns to perform nondimensionalization for simplicity.
\end{itemize}

### 2022-02-14 doc/reviews/ResponseToReviewer2.tex

\noindent
\comment{The abbreviation HAP is not defined in the text. I guess it stands for hydrophobic attraction potential.
}
\begin{itemize}
  \item Thank you for noticing this oversight. The definition of HAP has
    been added at its first occurrence in Section 3.1. 
\end{itemize}

\noindent
\comment{$u$ is used for both the velocity and the solutions of the
Laplace equation. Please use another variable for the scalar function
$u$.}
\begin{itemize}
  \item The velocity ${\bf u}({\bf x})$ introduced in the mobility problem (eqn. (2.1)--(2.3)) is in bold face and of a vector form. The scalar solution function $u$ is the solution of the screened Laplace equation boundary value problem (eqn. (2.7)--(2.9)). Therefore there is no duplication of usage in notation. In reponse to this point, in order to avoid confusions, we changed the scalar function to $\eta$.
\end{itemize}

### 2022-02-14 doc/reviews/ResponseToReviewer3.tex

In this work we use similar techniques for solving the integral equations when some boundaries are quite close to each other.  As the repulsive More potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids gives us confidence in the accuracy of the fluid flow in the thin space between the particles.

\item Change: We added a short paragraph to describe our methodology to capture the lubrication flow in the space between particles in close vicinity of each other in page, between lines \$\$\$ and \$\$\$.

\end{itemize}

\noindent
\comment{{\bf 2.} Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
  \item Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
which is different from the trends shown in panels (a) and (b). We showed the actual time evolution of $A^*$ and $\Delta$ and fitting curves in (a). 
The idea is to show that we can use the fitting data to acquire the numerical expected teminal 
reduced area $A^*_\infty$. Therefore the multiple frequencies during simulations have no correlations between
the output in (c) and (d).
\end{itemize}

@@

\noindent
\comment{{\bf 3.} Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about $4 \times R$. The authors are suggested to
double-check their model parameterization.}
\begin{itemize}
  \item Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated. Therefore the $x$-axis of Fig.~6 represents the time horizon in unit of $\mu$s and 
the $y$-axis represents the $y$ position of the centroid of the JP vesicle.
\end{itemize}

\noindent
\comment{{\bf 4.} In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
  \item We corrected the original Fig.~10 by plotting all continuous streamlines. We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
steps.
\end{itemize}
